Developing a preprint culture in biology

### 2012-10-05 ms.tex
Minor edits on the figshare section

Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an open server
that allows scientists to submit any research output: manuscript, figures,
datasets, videos, theses, presentations, and so on. There are no rules to limit
what constitutes a research output and, unlike arXiv, there is no endorser
system. All figshare content has a unique digital object identifier (DOI) like
any journal article, thus offering a permanent and stable link to the content.
A flexible tag system is used to classify each item. All content can be
commented and is licensed under the Creative Commons (CC-BY) license, except
datasets which are published under CC0. The CC-BY license grants rights to
\emph{copy, distribute, display and perform the work and make derivative works
based on it only if they give the author or licensor the credits in the manner
specified by these.}  CC0 is the most permissive license and effectively puts
the work in public domain (no rights reserved) or, if it is not possible in the
given jurisdiction, provides a simple permissive license.

One of the biggest advantage of figshare over arXiv is that is it not limited to
quantitative sciences. arXiv.org has sections on quantitative biology but might
not be appropriate for non-quantitative work. With its flexible approach to
preprints, figshare offers an important alternative to arXiv for empirical
biologists. Furthermore, by allowing all types of content, figshare arguably
provides an archive for early results (e.g.: figures, lab presentations).

>>>>

Figshare (\href{http://figshare.com/}{http://figshare.com/}) is an open server
that allows scientists to submit any research output: manuscripts, figures,
datasets, videos, theses, presentations, and so on. There are no rules to limit
what constitutes a research output and, unlike arXiv, there is no endorser
system. All figshare content has a unique digital object identifier (DOI) like
any journal article, thus offering a permanent and stable link to the content.
A flexible tag system is used to classify each item. All content
is licensed under the Creative Commons (CC-BY) license, except
datasets which are published under CC0. The CC-BY license grants rights to
\emph{copy, distribute, display and perform the work and make derivative works
based on it only if they give the author or licensor the credits in the manner
specified by these.}  CC0 is the most permissive license and effectively puts
the work in public domain (no rights reserved) or, if it is not possible in the
given jurisdiction, provides a simple permissive license.

One of the biggest advantage of figshare over arXiv is that is it not limited to
quantitative sciences. arXiv.org has sections on quantitative biology but might
not be appropriate for non-quantitative work. With its flexible approach to
preprints, figshare offers an important alternative to arXiv for empirical
biologists. Furthermore, by allowing all types of content, figshare arguably
provides an archive for early results (e.g.: figures, lab presentations).
figshare also supports commenting on preprints.
